Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-10 paper/ms.tex
Picked off another subsection in the methodology section of Carlyn's paper.

The process of mapping the \MESA\ models began by converting 
the \MESA\ model to a uniform grid of $4$~km resolution. \MESA\ 
quantities in zones with spacing less than $4$~km 
were mass-weighted averaged and a quadratic interpolation
was used to calculate quantities for the case of \MESA\ zones having
a spacing greater than $4$~km. At this point, 
abundances of nuclides from the \MESA\ models were aggregated
into the abundances tracked by the flame capturing scheme in
\FLASH.
The most abundant isotopes in the model were \C{12}, \Ox{16},
and \Ne{20}, which are symmetric (the number of neutrons 
equals the number of protons). Similarly to~\citet{willcoxetal2016}, 
other neutron-rich isotopes in the initial model were combined into 
\Ne{22}, which serves as a proxy for metallicty. The aggregation
account for the $Y_e$ of the full set of nuclides, \Ne{20} 
and \Ox{16} were constrained to be in the same ratio $R$ in both 
sets of abundances.

MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
matter. This means that the ratio of neutrons to protons in the nuclei
must be the same ratio as in the mesa profile. This is because the amount
of extra neutrons around is important when burning the star because that
determines how much neutron rich isotopes the burning produces.

>>>>

The process of mapping the \MESA\ models began by converting 
the \MESA\ model to a uniform grid of $4$~km resolution. \MESA\ 
quantities in zones with spacing less than $4$~km 
were mass-weighted averaged and a quadratic interpolation
was used to calculate quantities for the case of \MESA\ zones having
a spacing greater than $4$~km. At this point, 
abundances of nuclides from the \MESA\ models were aggregated
into the abundances tracked by the flame capturing scheme in
\FLASH.
The most abundant isotopes in the model were \C{12}, \Ox{16},
and \Ne{20}, which are symmetric (the number of neutrons 
equals the number of protons). Similarly to~\citet{willcoxetal2016}, 
other neutron-rich isotopes in the initial model were combined into 
\Ne{22}, which serves as a proxy for metallicty. The aggregation
account for the $Y_e$ of the full set of nuclides, \Ne{20} 
and \Ox{16} were constrained to be in the same ratio in both 
sets of abundances.

The original \MESA\ model was in equilibrium, but to ensure
the uniformly gridded model was in hydrostatic equilibrium we 
constructed the appropriate pressure profile. This was done by
integrating for the pressure in each zone from the central point up, 
accounting for the local acceleration of gravity, temperature,
composition, and the mass below and enclosed by the zone. As
with \citet{willcoxetal2016} we used
EOS routine from 
\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The 
Helmholtz EOS table used in \CASTRO\ is in the public BoxLib 
Microphysics repository at
  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit 
  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} As 
 with the models in \citet{willcoxetal2016},this procedure produced 
 a structure that was stable in \FLASH, with fluctuations in central
density less than $3\%$, for at least $5$ seconds with no energy
deposition.
